\section{Challenges in the smart grid}

\subsection{Security}
\todo{Wederom een schaamteloze kopie uit \cite{mcdaniel2009security}}

Although deploying the smart grid has enormous social and technical benefits, several security and privacy concerns arise. Because grid customers are connected over a vast network of computerised meters and infrastructure, they and the infrastructure itself become vulnerable to scalable network-borne attacks. These meters make excellent targets for malicious hackers, largely because vulnerabilities can easily be monetised. Compromised meters allow users to manipulate their usage data or energy costs. Customer fraud is not the only problem that arises, the costs of patching hundreds of millions of meters also plays a big role. 

Another big issue concerning the security of smart peripherals is the increased risk of large-scale attacks on the electrical grid. Meter bots, distributed denial-of-service attacks, usage loggers, smart meter root-kits, meter-based viruses, and other malware are almost certainly in these devices’ future. 

Lastly, privacy is a key concern in the smart grid. Energy use information stored at the meter and distributed thereafter acts as an information-rich side channel, exposing customer habits and behaviours. Certain activities, such as watching television, have detectable power consumption signatures. 

To deal with these issues, a broad effort is needed to investigate smart grid security and privacy. We can’t wait to determine whether current laws and technology sufficiently protects users and utilities. This effort results in laws that will help customers, utilities and vendors to assess risk, in turn dramatically increasing smart grid adoption. We must also plan with failure in mind. Complex software systems such as these are by nature going to have bugs, which means the industry must develop comprehensive recovery strategies to overcome these difficulties. 

\subsection{Demand side management}

The future smart grid needs to manage the supply and demand of energy effectively. If there is a too large discrepancy between the amount of energy that is available and the amount that is requested, either a lot of superfluous energy will be wasted, or power outages could occur.
So typically one would want to make sure the supply and demand of energy match as closely as possible at all times. This is easier said than done because not all power sources in the smart grid are constant. Wind turbines for instance yield varying amounts of energy depending on the weather conditions. The situation is further complicated by the fact that user demands also vary from time to time. In the evening hours a lot of energy is being used, but during the nighttime energy consumption is at a low. The grid however needs to be prepared for the worst, and should be able to supply everyone with energy, even during peak hours.

In the following sections multiple factors and tools that can influence the supply and demand of energy are discussed. This way the peaks in demand and the dips supply can be smoothened, and thus improve the reliability of the smart grid.

\subsubsection{Smart users, adaptation of human behavior}

A way to manage the peaks in user demands, is by making the user aware of them. Theoretically speaking a peak in energy demand can be reduced (or entirely avoided) if all users spread out their energy usage over the course of the day. Practically speaking however it is very hard to change human behaviour.
In a study where users were asked if they would be willing to reduce their energy demands by showering for a maximum of five minutes during the morning most participants reacted negatively. They felt like the morning shower was part of their morning routine and having a device installed that would turn of the (hot) water after five minutes threatened the relaxation and comfort they experienced when taking said shower. 

\todo{Add: rode en groene ledjes, peer comparison feedback methods}

\subsubsection{Smart tariffs}

Humans aren’t very eager to change their energy consumption patterns on their own. They need incentive in order to be enticed to change their ways. Smart pricing is a form of such an incentive. Peak rates in wholesale energy prices are already being used, however they go by unnoticed. Most end user are charged with an average price, and unaware of their energy usage during peak hours, they don’t change their consumption patterns. 

Users need to be made more aware of their energy usage during peak hours, and they need to make manual changes or energy consumption scheduling should be (partially) automated.

\subsubsection{Smart meters, insight in enery usage and supply}

\todo{Expand this section}

Aside from diminishing peaks in user power demand,the smart meter has another potential benefit. It could help reduce the impact of dips in energy supply. The smart meter is capable of temporarily decreasing the load on the grid, or even supplying energy to the grid, by discharging the battery of for instance an EV and thus creating a power surplus. If there are enough smart meters connected to the grid with these capabilities, the effects of a reduced energy flow can be entirely negated.